### 2015-05-16 ase-2015-tex/approach.tex
started replacing other wordings with path condition, reworked value set function explanation paragraph

The value set computation is local: it only considers constraint
locations on the reference $\cfgnt{r}$. Further, it only includes
constraints that are feasible under the current path condition
$\phi_g$. It also ensures that the access path is valid. There is a
constraint $\phi$ from the base reference $r$ and a given
location. Once a location $l$ is selected its field $\cfgnt{f}$ is
accessed to get another reference $r^\prime$, and from that reference
there is a set of locations each with a constraint. The first
constraint $\phi$ from the base reference plus this second constraint
to the actual location of the field $\phi^\prime$ comprise the access
path. For each member of the value set, these constraints together
with the global path constraint must be satisfied on some aliasing
assignment. % \nsr{neha: this para needs work -- flow and content}

>>>>

For a reference $\cfgnt{r}$ and field $\cfgnt{f}$, the value set function computes 
the set of locations that the field could dereference to, paired with a local and valid access path constraint
that is feasible under the current path condition $\phi_g$.
The access path constraint is the union of two local constraints: 
the constraint $\phi$ from dereferencing $\cfgnt{r}$ to location $\cfgnt{l}$, 
and the constraint $\phi^\prime$ from dereferencing the field $\cfgnt{f}$ of the location $\cfgnt{l}$ to the actual location of the field, $\cfgnt{l}^\prime$. 
This access path constraint, paired with location $\cfgnt{l}^\prime$, is a member of the value set only if its union with the path condition is satisfiable, ensuring that the access path is valid and feasible under the path condition.
 % \nsr{neha: this para needs work -- flow and content tao: worked on the flow}

### 2015-05-16 ase-2015-tex/summary-heap.tex
Added new intro figure.
started replacing other wordings with path condition, reworked value set function explanation paragraph

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.2]{../figs/simple_heap_scratch.png}
\end{center}
\caption{Example Heap (scratch image, not for publication!)}
\label{fig:exampleHeap}
\end{figure}

@@

The state of the machine, $\cfgnt{s}$, includes the program
registry, $\mu$, a pair of functions defining the heap
$\lp\cfgnt{L}\ \cfgnt{R}\rp$, a constraint, $\phi$, defined over
references in the heap, the environment, $\eta$, for local variables,
and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation.  The
more complex structures, such as the environment and heap, are defined
as lists that start with empty, \cfgnt{mt}. These lists are treated as
partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
$\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores
temporary computation, and keeps track of the next computation. For
example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
expression for the object reference on which the field $\cfgnt{f}$ is
going to be accessed. Once the field access is complete, the machine
continues with $\cfgnt{k}$.

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.5]{../figs/simple_heap_scratch.pdf}
\end{center}
\caption{Example Symbolic Heap}
\label{fig:exampleHeap}
\end{figure}

@@

The state of the machine, $\cfgnt{s}$, includes the program
registry, $\mu$, a pair of functions defining the heap
$\lp\cfgnt{L}\ \cfgnt{R}\rp$, the path condition, $\phi$, a constraint defined over
references in the heap, the environment, $\eta$, for local variables,
and the continuation $\cfgnt{k}$. The registry never changes so it is
omitted from the state tuple in the rest of the presentation.  The
more complex structures, such as the environment and heap, are defined
as lists that start with empty, \cfgnt{mt}. These lists are treated as
partial functions so $\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference
$\cfgnt{r}$ associated with variable $\cfgnt{x}$. The notation
$\eta^\prime = \eta[\cfgnt{x} \mapsto \cfgnt{v}]$ defines a new
partial function $\eta^\prime$ that is the same as $\eta$ except that
the variable $\cfgnt{x}$ now maps to $\cfgnt{v}$. The continuation
$\cfgnt{k}$ indicates where the hole, $\cfgt{*}$, is located, stores
temporary computation, and keeps track of the next computation. For
example, the continuation $\lp\cfgt{*}\ \cfgt{\$}\ \cfgnt{f}
\rightarrow \cfgnt{k}\rp$ indicates that the machine is evaluating the
expression for the object reference on which the field $\cfgnt{f}$ is
going to be accessed. Once the field access is complete, the machine
continues with $\cfgnt{k}$.
